The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 Discussion/lessons.tex
fixed todos in discussion

\subsection{Lessons Learned}
From our results, it is evident that \ehi vulnerabilities exist in the wild.
% Adam: Sai, I don't understand this math. The 1.46% number is calculated based on the number of forms we were able to fuzz with a malicious payload. This isn't the same as the number of websites. But, using 673/21675680 is not good either because that is # of URLs and it seems like the number you have here is websites. What we need is what % of *websites* (probably estimated as domains) did we find to be vulnerable out of *all* websites/domains that we found. When we use this number, we need to be clear what it is that we are using.
Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of websites on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successDelta\ percent (the occurrence rate of \ehi vulnerability as found by our system) of that number, this yields 14,875,413 websites. Of course, extrapolation in this way is not an accurate measure of the prevalence of \ehi vulnerabilities. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

% Adam: Please add a citation to a CAPTCHA paper
	A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications. CAPTCHAs pose a very difficult problem for our system to exploit \ehi, even if it is present.

@@

\texttt{To header injection} allows an attacker to extract information that should be private,
% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message. I thought to header injection just controls the TO field, not the message contents. 
and in some of these cases, able to inject enough data to spoof the first few lines of the \email message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.

>>>>

\subsection{Lessons Learned}
From our results, it is evident that \ehi vulnerabilities exist in the wild.
% Adam: Sai, I don't understand this math. The 1.46% number is calculated based on the number of forms we were able to fuzz with a malicious payload. This isn't the same as the number of websites. But, using 673/21675680 is not good either because that is # of URLs and it seems like the number you have here is websites. What we need is what % of *websites* (probably estimated as domains) did we find to be vulnerable out of *all* websites/domains that we found. When we use this number, we need to be clear what it is that we are using. -- FIxed this to be clear.
Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of domains on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successWebsitesDelta percent (the occurrence rate of \ehi vulnerability calculated from vulnerable domains as found by our system to total number of domains crawled) of that number, this yields 295,693 domains. Of course, extrapolation in this way is not an accurate measure of the prevalence of \ehi vulnerabilities. However, even with as few as a thousand domains affected by this vulnerability, it can still have a disastrous impact on these domains, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

@@

% Adam: Please add a citation to a CAPTCHA paper - DONE.
	A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications. CAPTCHAs~\cite{captchas2} pose a very difficult problem for our system to exploit \ehi, even if it is present.

@@

\texttt{To header injection} allows an attacker to extract information that should be private,
% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message. I thought to header injection just controls the TO field, not the message contents. - Fixed, my bad. DONE.
and in some of these cases, able to inject enough data to spoof other headers of the \email message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on \ehito forms, while spoofing using \texttt{To header injection} was possible on \ehitoxcheck forms.
